---
title: "Using jsPsych and cognition.run"
subtitle: "Session 2 - intermediate"
author: "James Brand"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmdformats::readthedown:
    pandoc_args: "--highlight-style=my.theme"
    highlight: pygments
    toc_float: true
    code_download: true
    toc_depth: 3
    collapsed: false
    df_print: paged
    lightbox: TRUE
    gallery: TRUE
    css: "css/style.css"
    
---

```{r echo=FALSE, warning=FALSE}
library(slickR)
library(htmltools)
library(xaringanExtra)
library(rmarkdown)
library(fontawesome)
library(bsplus)

```

```{r setup, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = FALSE,
                      comment = NA)

knitr::knit_hooks$set(
  message = function(x, options) {
     paste('<button type="button" class="collapsible1"><strong>',
     fa(name = "circle-info"),
     ' more info</strong></button>', '<div class="content1"><p>',
     gsub('##', '\n', x),
     '</p></div>',
     sep = '\n')
   })

codeblock = function(x, options) {
     cat(paste('<div class="codeblock">',
     paste0(x),
     '</div>',
     sep = '\n'))
   }

```

---

## `r fa("language")` Translations available

Disclaimer: may not be very accurate...

<div id="google_translate_element"></div>

---

# Worksheet overview

## `r fa("crosshairs")` Aims

By the end of this worksheet you should be able to:

- **program** your own experiments in jsPsych
- **host** the experiment online using cognition.run
- **use** the participant data for analysis
- **apply** the basic skills you have learnt for your own purposes
- **learn** some extra skills such as HTML, javascript, CSS and JSON

## `r fa("user-graduate")` Pre-requisites

To complete the aims you will need to:

- **follow** this worksheet
- **ask** questions if you are not sure/be able to google
- **have** a working computer and internet connection
- **be patient** when things do not work

You do not need to:

- have any **programming knowledge**
- have high **computer literacy**
- know anything about **jsPsych, cognition.run, html, css or javascript**
- be a **linguist**

## `r fa("folder-tree")` Structure

The worksheet will go through the following sections:

- Introducing cognition.run

    - creating an account
    - considerations when using it
    - familiarisation with the interface
<br/><br/>
- Introducing jsPsych

    - what it is
    - considerations when using it
    - using official documentation
<br/><br/>
- Running experiments

    - integrating JsPsych with cognition.run
    - familiarisation with JsPsych programming
    - building a very simple experiment

In the next sessions we will cover:

- building a proper experiment
- using stimuli files
- customising plugins
- customising appearance
- working with the data

---







```{r echo=FALSE, eval=TRUE, warning=FALSE}
htmltools::tags$script(src = "js/translate.js")
# htmltools::tags$script(src = "js/infobox.js")
htmltools::tags$script(src="//translate.google.com/translate_a/element.js?cb=googleTranslateElementInit")

htmltools::tagList(
  xaringanExtra::use_clipboard(
    button_text = "<i class=\"fa fa-clipboard\" style=\"font-size: 25px\"></i>",
    success_text = "<i class=\"fa fa-check\" style=\"color: #90BE6D; font-size: 25px\"></i>",
  ),
  rmarkdown::html_dependency_font_awesome()
)

```

```{js echo=FALSE, eval=TRUE}
var coll = document.getElementsByClassName("collapsible1");
var i;

for (i = 0; i < coll.length; i++) {
  coll[i].addEventListener("click", function() {
    this.classList.toggle("active1");
    var content = this.nextElementSibling;
    if (content.style.maxHeight){
      content.style.maxHeight = null;
    } else {
      content.style.maxHeight = content.scrollHeight + "px";
    }
  });
}

```
